IFA Comparison of Noncognitive Skills \\ BCS and MCS

### 2018-04-12 codes/R/cohorts_nc.Rnw
add sequential decomposition graphs

<<READ, cache=FALSE >>=
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/1_load.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/2_efa.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_inv_main.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_inv_aux.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_inv_fit.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/4_scores.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/4_scores_aux.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/5_graphs.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/6_ineq.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/7_counterf.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/7_counterf_graphs.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/7_counterf_tabs.R")

@@

@@

\clearpage
\bibliographystyle{chicago}
%\bibliography{/Users/giacomomason/Documents/BibTeX/Papers-cohorts_nc}
\bibliography{/Users/giacomomason/Dropbox/Zotero/cohorts.bib}

>>>>

<<READ, cache=FALSE >>=
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/1_load.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/2_efa.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_inv_main.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_inv_aux.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_inv_fit.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/4_scores.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/4_scores_aux.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/5_graphs.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/6_ineq.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/7_counterf.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/7_counterf_graphs.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/7_counterf_tabs.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/7_counterf_seqdec.R")

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% COUNTERFACTUAL DECOMPOSITIONS

<<COUNTERF_SEQDEC_PREP>>=
# data for decomposition plots
@

<<COUNTERF_SEQDEC_PLOT>>=
# decomposition plots
@

\begin{landscape}
\begin{figure}
<<COUNTERF_SEQDEC_EXT, dependson='COUNTERF_SEQDEC_PREP', dev='tikz', fig.height=10, fig.width=16, out.width='1\\linewidth'>>=
cfp.seqdec.ext
@
\caption{Counterfactual sequential decomposition -- externalising skills}\label{fig:counterf_seq_ext}
{\scriptsize \emph{Notes}: \par}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
<<COUNTERF_SEQDEC_INT, dependson='COUNTERF_SEQDEC_PREP', dev='tikz', fig.height=10, fig.width=16, out.width='1\\linewidth'>>=
cfp.seqdec.int
@
\caption{Counterfactual sequential decomposition -- internalising skills}\label{fig:counterf_seq_int}
{\scriptsize \emph{Notes}: \par}
\end{figure}
\end{landscape}

@@

\clearpage
\bibliographystyle{chicago}
\bibliography{/Users/giacomomason/Dropbox/Zotero/cohorts.bib}
